---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# reportesAPI

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/reportesAPI)](https://CRAN.R-project.org/package=reportesAPI)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/calderonsamuel/reportesAPI/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/calderonsamuel/reportesAPI/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/calderonsamuel/reportesAPI/branch/main/graph/badge.svg)](https://app.codecov.io/gh/calderonsamuel/reportesAPI?branch=main)
<!-- badges: end -->

The goal of reportesAPI is to be able to get data from a Reportes instance for use in the app or in analysis.

The user should also have an `.Renviron` file containing the following variables:

- `DB_HOST`
- `DB_NAME`
- `DB_USER`
- `DB_SECRET`
- `DB_PORT`
- `REPORTES_EMAIL` (Optional)

The package asumes you are using RMariaDB for data storage.

## Installation

You can install the development version of reportesAPI from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("calderonsamuel/reportesAPI")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(reportesAPI)

man <- DBManager$new()
```

When fetching data, instead of returning a data.frame, by default we get a tibble.

```{r cars}
man$db_get_query("SELECT user_id, time_last_modified FROM users")
```

To start an instance of `AppData` is necessary to provide an email. This will not be done here for security reasons.
