---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# reportesAPI

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/reportesAPI)](https://CRAN.R-project.org/package=reportesAPI)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of reportesAPI is to be able to get data from a Reportes instance for use in the app or in analysis.

The user should also have an `.Renviron` file containing the following variables:

- `DB_HOST`
- `DB_NAME`
- `DB_USER`
- `DB_SECRET`
- `DB_PORT`
- `REPORTES_EMAIL` (Optional)

The package asumes you are using RMariaDB for data storage.

## Installation

You can install the development version of reportesAPI from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("calderonsamuel/reportesAPI")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(reportesAPI)

man <- DBManager$new()
```


```{r cars}
summary(cars)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
